Counterexample-guided Synthesis \\ of Closed-loop Digital Control Systems

### 2016-09-24 paper/paper.tex
add cruise control model

%
\begin{equation}
\label{cruise-control-g1}
G_{1}(z)=\frac{1.51z-1.3586}{z-1}.
\end{equation} 
%
\begin{equation}
\label{cruise-control-c1}
C_{1}(z)=\frac{0.0264}{z-0.998}.
\end{equation}

>>>>

The discrete plant of a cruise control model with time step
of 0.2s for the car accounting for rolling friction, aerodynamic drag, 
and gravitational disturbance force is considered~\cite{Astrom08} 
as follows
%
\begin{equation}
\label{cruise-control-c1}
G(z)=\frac{0.0264}{z-0.998}. \nonumber
\end{equation}

Two proportional-integral (PI) controllers are designed by Wang {\it et al.} 
for the cruise control plant $G(z)$ \cite{DBLP:conf/hybrid/WangGRJF16}, 
which has the following mathematical model
%
\begin{equation}
\label{cruise-control-g1}
C_{1}(z)=\frac{1.51z-1.3586}{z-1}, \nonumber
\end{equation} 
%
\begin{equation}
\label{cruise-control-g2}
C_{2}(z)=\frac{2.72z^2 - 4.153z + 1.896}{1.0z^2 - 1.844z + 0.8496}. \nonumber
\end{equation}
